        %-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Test Tools Software Developer} % Job title
    {Valeo Vision Systems. - Automotive supplier and partner to automakers worldwide} % Organization
    {Co Galway, Ireland} % Location
    {Nov. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development in C++ for automotive systems based on Windows.}
        \item {Developing test procedures and validation plans for Advanced Driver Assistance Systems (ADAS)\\
    features and Autonomous Vehicles.}
        \item {Working with testing methodologies and work with vehicle, hardware-in-the-loop, software-in-the-loop\\
    to validate features.}
        \item {Experience with sensing systems such as cameras, radar, lidar, GPS, IMUs.}
        \item {Developing software components integrating new applications to automotive bus and\\
    hardware architectures using Automotive Data and Time Triggered Framework (ADTF).}
        \item {Working with Team Forge software management platform integrated with GIT.}
        \item {Experience with graphics library OpenCV.}
        \item {Experience developing UI applications using Qt.}
        \item {Adapting legacy code to continuous integration with Jenkins.}
        \item {Experience with SOAP, REST, RPC services and JSON/XML parsing tools.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Developer} % Job title
    {Khomp Co., Ltd. - Solutions of convergence between computers and telephony} % Organization
    {Florianópolis, Brazil} % Location
    {Feb. 2017 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Head of zero-touch provisioning platform project at stage one. \\
	It allows installing the hardware directly into the environment without manual intervention.}
        \item {Development in C++ for telecommunication systems based on embedded Linux.}
        \item {Front-end development using jQuery.}
        \item {Python development for automated tests with Gherkin/Selenium.}
        \item {Python development for server-side applications.}
        \item {Working with GIT integrated with Gitlab.}
        \item {Experience in Redmine as task tracking software.}
        \item {Automating compilation processes with Scons.}
        \item {Working with Conan C/C++ package manager.}
        \item {Work methodology based on Scrum.}
        \item {Experience building web API JSON-RPC.}
        \item {Working with VOIP systems, Asterisk PBX, TDM, and VoIP protocols.}
        \item {Writing feature documentation for user manual and testers.}
        \item {Customer training and presentation about the company products.}
        \item {Implementing features to User Media Gateway, that aims convergence VoIP-TDM telephony.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Developer} % Job title
    {Hexagon Agriculture Co., Ltd. - Management system for precision agriculture} % Organization
    {Florianópolis, Brazil} % Location
    {Sep. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development in C++ for precision agriculture system based on embedded Linux.}
        \item {Software-Hardware integration.}
        \item {Working with GIT integrated with Bitbucket.}
        \item {Experience developing UI applications using Qt.}
        \item {Using of JIRA as task tracking software.}
        \item {Python development to data interchange and software-hardware interoperability.}
        \item {Implementation of Linux Inter-Process Communications with D-Bus.}
        \item {Head of board testing project. Aiming the improvement of board test process.}
        \item {Experience with graphics library OpenGL.}
        \item {Working with Scrum tools.}
        \item {Automating compilation processes with Cmake.}
        \item {Writing feature documentation for the user manual.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher and Software Developer} % Job title
    {Reivax Co., Ltd. - Systems and solutions for the control of energy generation} % Organization
    {Florianópolis, Brazil} % Location
    {Jul. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research and development for a Brazilian government project.}
        \item {Development in C++ for systems and solutions for power generation management.}
        \item {Working with Delphi language to improve a legacy system.}
        \item {Bug fixes and development of graphical user interfaces.}
        \item {Development of embedded system software.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {C++ Developer III} % Job title
    {Audaces Co., Ltd. - Fashion technological innovation} % Organization
    {Florianópolis, Brazil} % Location
    {Aug. 2012 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bug fixes and improvements graphical user interfaces.}
        \item {Refactoring a monolithic legacy system.}
        \item {Adapting legacy code to continuous integration with Jenkins.}
        \item {Adapting legacy code to CMake build systems.}
        \item {Working with GIT.}
        \item {Writing automated tests.}
        \item {Experience with graphics library OpenCV.}
        \item {Knowledge of Agile methodology.}
      \end{cvitems}
    }

    \cventry
    {C++ Developer II} % Job title
    {} % Organization
    {} % Location
    {Jan. 2008 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improving code from C++ to C++11.}
        \item {Refactoring legacy code into MVC design.}
        \item {Bug fixing and improvement of code.}
        \item {Experience developing UI applications using Qt.}
        \item {Using of Boost library.}
        \item {Working with SVN and writing automated tests.}
      \end{cvitems}
    }

    \cventry
    {C++ Developer I} % Job title
    {} % Organization
    {} % Location
    {Oct. 2006 - Jan. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Head of image processing project – Digiflash (scanning a pattern from a digital picture).}
        \item {Researching in image processing, pattern recognition (neural networks, cross-correlation).}
        \item {Bug fixes in CAD/CAM system.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
