%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A Guide for CV} % Title
    {
      \begin{cvitems} % Description(s)
        \item {Experienced professional with passion for software development.}
        \item {Experience in software development for Linux and Windows platforms.}
        \item {Designing and developing in C++ as the main language and Python skills.}
        \item {Embedded systems based on Linux.}
        \item {Version control system and repositories management services. Skills: Git, Github, Gitlab, Bitbucket.}
        \item {Experience with task tracking platforms like JIRA and Redmine.}
        \item {User interface development toolkit Qt.}
        \item {JavaScript front-end experience using jQuery library.}
        \item {Improving/refactoring legacy code implementing continuous integration, unit and acceptance tests.\\
        Skills: Unit Tests, Acceptance Tests, BDD, TDD, CI, MVC, Jenkins, GoogleTest, Catch, Behave,
        Gherkin/Selenium.}
        \item {Experience with graphics libraries OpenGL and OpenCV.}
        \item {Automating the process of compilation with build systems. Skills: CMake, Scons.}
        \item {Libraries that provide support for tasks and structures. Skills: Boost, STL, Python modules.}
        \item {Experience with Conan C/C++ package manager to create, test and release code.}
        \item {Knowledge in persistent storages and SQL databases. Skills: Postgres, MySQL, SQLite, Redis,
        MongoDB.}
        \item {Knowledge of data interchange formats and transfer architecture. Skills: JSON, XML, JSON-RPC,
        Rest.}
        \item {Experience with Docker automating the deployment of applications.}
        \item {Knowledge in TDM and VoIP protocols.}
        \item {Working experience with VoIP systems. Skills: SIP, Asterisk PBX.}
        \item {Customer training and presentation skills.}
        \item {Experience using Scrum/Agile tools.}
        \item {Writing product documentation, manuals, and guides for testers and customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
